\Large \bf 6.829 Final Project: A comparison of bit-rate selection algorithms

### 2013-05-14 paper/paper.tex
added plots

There are three main classes of bit rate adaptiation protocols: frame-based, SNR-based, and cross-layer protocols. Frame-based protocols measure the fraction of sucessfully received protocols. SNR protocols make decisions based on the estimated Signal to Noise ratio. Cross-layer protocols use SoftPHY data from the physical layer. The most commonly implemented protocols on today's networks are frame based, because SNR protocols perform poorly [CITATION HERE], and cross-layer protocols cannot be deployed on current networks because they violate the network layering abstration.

@@

We used a trace-based approach to collect data, and then replayed that data to the rate-selection algorithms using a Python framework. Th

@@

At this point, we decided to take a different approach and use an approach similar to that used in Sprout.

@@

Yeee haw.
\begin{figure}[htb]
  \hspace{-.75em}\includegraphics[width=3.5in]{constant.png}\vspace{-0em}
  \caption{Throughput of using a constant 802.11b/g bitrate in an MIT basement.}
\end{figure}

>>>>

There are three main classes of bit rate adaptiation protocols: frame-based, SNR-based, and cross-layer protocols. Frame-based protocols measure the fraction of sucessfully received protocols. SNR protocols make decisions based on the estimated Signal to Noise ratio. Cross-layer protocols use SoftPHY data from the physical layer. The most commonly implemented protocols on today's networks are frame based, because SNR protocols perform poorly~\cite{samplerate}, and cross-layer protocols cannot be deployed on current networks because they violate the network layering abstration.

@@

We used a trace-based approach to collect data, and then replayed that data to the rate-selection algorithms using a Python framework.

@@

At this point, we decided to take a different approach and use an approach similar to that used in Sprout~\cite{sprout}.

@@

\begin{figure}[htb]
  \hspace{-.75em}\includegraphics[width=3.5in]{constant.png}\vspace{-0em}
  \caption{Throughput of using a constant 802.11b/g bitrate in an MIT basement.}
\end{figure}
